%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package
\usepackage{graphicx}  % For including images
\usepackage{ragged2e}  % For justified text
\usepackage{fancyhdr}  % For better footer
\pagestyle{fancy}

% Footer settings
\pagestyle{fancy}
\fancyhf{} % Clear existing header/footer
\fancyfoot[L]{September 15, 2024} % Left
\fancyfoot[C]{} % Center
\fancyfoot[R]{Page: 1/1} % Right
\renewcommand{\headrulewidth}{0pt} % No line in header
\renewcommand{\footrulewidth}{0pt} % Line in footer

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.1}
  \item {\Calluna (+84) 0792-252-902}  % Phone number
  \item {\Calluna khoacao.dev@gmail.com}  % E-mail address
  \item {\Calluna Ho Chi Minh City, Vietnam}  % Address
\end{flushright}\vspace{-60pt}

\begin{flushleft}
  %\setstretch{0.1}
  {\Calluna \fontsize{30pt}{0pt}\selectfont \textsc{KHOA DANG CAO}} \\
  \vspace{5pt}
  {\Calluna \fontsize{10pt}{30pt}\selectfont \textsc{Back-end Developer} \hspace{5pt} $\cdot$ \hspace{5pt} \textsc{Researcher} \hspace{5pt} $\cdot$ \hspace{5pt} \textsc{Peer Tutor}}

  \noindent
    \begin{justify}
    \setstretch{1.1}
    \textit{``As a passionate 19-year-old Computer Science student specializing in web development, software development, and AI engineering, I am actively involved in innovative projects such as digitization systems and machine learning models. My objective is to leverage my technical skills and innovative ideas to make a significant impact in the tech industry while seeking advanced opportunities abroad. Supported by a strong passion for research and a proactive approach to problem-solving, I am eager for the opportunities ahead.''}
    \end{justify}
    \noindent\rule{\textwidth}{0.3pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Birmingham City University}{Birmingham, UK}
  {Bachelor of Science with Honours in Computer Science}{2023 - 2026 \footnotesize{\textit{(expected)}}}
  {International Joint Program with University of Information Technology, VNU-HCM}
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{
\projHeading
{\textbf{Automated Digitization System for Vietnam Birth Certificates}}
{Database and Web Application Development Course Final Project} {2024.07 - 2024.08}

\projHeading
{\textbf{Spam Message Detector Machine Learning Model}}
{Youth Digital Citizen Challenge 2024: Digital Security Hackathon} {2024.04 - 2024.04}

\projHeading
{\textbf{Notecommit: A Collaborative Note-Taking Application}}
{Innovation Project Course Final Project} {2024.02 - 2024.05}

\projHeading
{\textbf{May Tinh Cu - Tri Thuc Moi (Old Computers - New Insights)}}
{Repurposes used hardware to create new educational opportunities} {2024.01 - Ongoing}

\projHeading
{\textbf{Servi: A Platform Connecting Freelancers and Clients}}
{The 2023 UIT Creative Startup Ideas Hackathon} {2023.12 - 2023.12}

\projHeading
{\textbf{17.Blog: A New Social Media with Blog-Oriented}}
{Website Design and Development Course Final Project} {2023.10 - 2024.01}
}

% -------------------- INTERNSHIPS --------------------
\sectionBlock{
\section{Internships}
}{
\internHeading
  {NHAT NGUYEN Tech Co., Ltd (DigiSER)}{HCMC, Vietnam}{2024.04 - 2024.07}
  {A digitalisation provider offering data digitization, image processing, and data labelling.}
\itemListStart
  \myItem{Worked as a Front-end and Back-end Web Developer}
  \myItem{Build and develop web applications for digitising services.}
  \myItem{Research and analyse types of Vietnam civil status documents.}
  \myItem{Technologies used: Django, ReactJS, Tailwind CSS}
\itemListEnd
}

% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
\section{Awards\\and\\Honors}
}{
\awardListStart
\justifying
\item \emph{Certificate of Appreciation}, Binh Thuan Provincial Youth Union \hfill 2024.07
\item \emph{Merit-Based Scholarship}, University of Information Technology \hfill 2024.04
\item \emph{Most Favourite Startup Project}, UIT Creative Startup Ideas Hackathon \hfill 2023.12
\item \emph{Second Prize}, UIT Excellent Programs Team Building Competition \hfill 2023.10
\awardListEnd
}

% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Languages}: Vietnamese (native), English (IELTS Score of 6.0).
\item \emph{Programming}: Python, C++, Java, JavaScript, Bash.
\item \emph{Technologies}: Flask, Django, FastAPI, ReactJS, PostgreSQL.
\item \emph{Tools}: Github, Adobe Illustrator, Adobe Photoshop, Adobe Premiere Pro.
\item \emph{Others}: Designing, Information Lookup, AI Prompting, Problem Solving, Leadership.
\skillListEnd
}

\end{document}
